---
title: "HDX RT_interpolation"
output: RT interpolation
---

Loading necessary libraries

```{r}
library(dplyr)
library(tidyverse)
library(ggpubr)
```

Loading necessary PLGS files. Load file using short LC gradient.

```{r}
PLGSshort=read.csv(file.choose())
```

Load PLGS file using long LC gradient.

```{r}
PLGSlong=read.csv(file.choose())
```

Filter PLGS files to only use "good" peptides. User can add/modify additional filters here if needed.
Filters used:
  - Minimum score: 6.62
  - Minimum products: 2
  - Minimum consecutive products: 1
  - Minimum intensity: 1000
  - Minimum sequence length: 5
  - Maximum sequence length: 30
  - Maximum MH+ error (ppm): 5
  - Minimum sum intensity for products: 472
  - Minimum products per amino acid: 0.11

```{r}
PLGSshort = PLGSshort %>% filter(peptide.score >=6.62, peptide.MatchedProducts >=2, peptide.ConsectiveMatchedProducts >=1, precursor.inten >1000, peptide.seqLength >=5, peptide.seqLength <=30, abs(peptidePrecursor.deltaMhpPPM)<=5, peptide.MatchedProductsSumInten >=472,(peptide.MatchedProducts/peptide.seqLength)>=0.11)

PLGSlong = PLGSlong %>% filter(peptide.score >=6.62, peptide.MatchedProducts >=2, peptide.ConsectiveMatchedProducts >=1, precursor.inten >1000, peptide.seqLength >=5, peptide.seqLength <=30, abs(peptidePrecursor.deltaMhpPPM)<=5, peptide.MatchedProductsSumInten >=472,(peptide.MatchedProducts/peptide.seqLength)>=0.11)
```

Find common peptides in both filtered PLGS files and create single dataFrame with both RTs.

```{r}
merge_ALL=full_join(PLGSlong %>% mutate(id=row_number()), PLGSshort) %>% group_by(peptide.seq, precursor.retT) %>% summarise () %>%
  group_by(peptide.seq) 

merge_ALL=merge_ALL[merge_ALL$peptide.seq %in% merge_ALL$peptide.seq[duplicated(merge_ALL$peptide.seq)],]

merge_ALL=merge_ALL %>%
  group_by(peptide.seq) %>%
  mutate(duplicate = ifelse(n() > 1, precursor.retT, NA)) %>% filter(duplicated(peptide.seq)|n()==1)

colnames(merge_ALL) = c("sequence", "RT_long","RT_short")
```

Fit the data to a linear line, and create plot with equation and squared R.

```{r}
fit <- lm(RT_long ~ RT_short, data = merge_ALL)

plot = ggplot(merge_ALL, aes(x=RT_short,y=RT_long))+geom_point()+
  geom_smooth(method=lm,se=FALSE, fullrange=TRUE)+
  annotate("text",x=6,y=30,label=paste("y=",signif(fit$coefficients[2],digits=4)," x + (",signif(fit$coefficients[1],digits=4),")"))+
  annotate("text",x=6,y=27,label=paste("R^2 =",signif(summary(fit)$r.squared,digits=4)))

plot

#install.packages("ggtrendline")
#library(ggtrendline)
#ggtrendline(x,y,model="exp3P",linecolor="blue",CI.fill=NA,linewidth=1)+geom_point(aes(x,y))+theme_bw()
```

Interpolate new RTs for all peptides and export as new .csv file and plot

```{r}
PLGSlong_newRT=PLGSlong        
PLGSlong_newRT$precursor.retT=(PLGSlong_newRT$precursor.retT-fit$coefficients[1])/fit$coefficients[2]

write.csv(PLGSlong_newRT,"PLGSlong_newRT.csv", row.names=FALSE)
ggsave("RTplot.png",plot)
```

